% REFERENCES
% ══════════════════════════════════════════════════════════════
\ifdefined\withappendix\else
\balance % balance the columns on the last page of references
\fi
\bibliographystyle{ACM-Reference-Format}

{
\ifdefined\compactappendixrefs
\scriptsize
\fi
\begin{thebibliography}{52}
\ifdefined\compactappendixrefs
\setlength{\itemsep}{0pt}
\setlength{\parsep}{0pt}
\setlength{\parskip}{0pt}
\fi

\bibitem[Anic et~al.(2025)]{anic2025chatgpt}
Anic, N., Barbon, A., Seiz, R., and Zarattini, C. (2025).
\newblock {ChatGPT} in systematic investing: Enhancing risk-adjusted returns with {LLMs}.
\newblock \emph{arXiv preprint arXiv:2510.26228}.

\bibitem[Bryzgalova et~al.(2025)]{bryzgalova2025forest}
Bryzgalova, S., Pelger, M., and Zhu, J. (2025).
\newblock Forest through the trees: Building cross-sections of stock returns.
\newblock \emph{The Journal of Finance}, 80(5):2447--2506.

\bibitem[Cheng and Chin(2024)]{cheng2024aapm}
Cheng, J. and Chin, P. (2024).
\newblock {AAPM}: Large language model agent-based asset pricing models.
\newblock \emph{arXiv preprint arXiv:2409.17266}.

\bibitem[Cheng et~al.(2024)]{cheng2024chatgptfactor}
Cheng, Y., Zeng, Y., and Zou, J. (2024).
\newblock Harnessing {ChatGPT} for predictive financial factor generation: A new frontier in financial analysis and forecasting.
\newblock \emph{The British Accounting Review}, 101507.

\bibitem[Chung et~al.(2025)]{chung2025mvecf}
Chung, M., Lee, J., Lee, Y., and Kim, W.~C. (2025).
\newblock Mean variance efficient collaborative filtering for stock recommendations.
\newblock \emph{Proceedings of the 6th ACM International Conference on AI in Finance (ICAIF '25)}, pages 806--813. arXiv:2306.06590.

\bibitem[Ding et~al.(2025)]{ding2025tradexpert}
Ding, Q., Shi, H., Guo, J., and Liu, B. (2025).
\newblock {TradExpert}: Revolutionizing trading with mixture of expert {LLMs}.
\newblock \emph{ICLR 2025 Workshop on Advances in Financial AI}. arXiv:2411.00782.

\bibitem[Carhart(1997)]{carhart1997persistence}
Carhart, M.~M. (1997).
\newblock On persistence in mutual fund performance.
\newblock \emph{The Journal of Finance}, 52(1):57--82.

\bibitem[Fama and French(1993)]{fama1993common}
Fama, E.~F. and French, K.~R. (1993).
\newblock Common risk factors in the returns on stocks and bonds.
\newblock \emph{Journal of Financial Economics}, 33(1):3--56.

\bibitem[Fama and French(2015)]{fama2015fivefactor}
Fama, E.~F. and French, K.~R. (2015).
\newblock A five-factor asset pricing model.
\newblock \emph{Journal of Financial Economics}, 116(1):1--22.

\bibitem[Fatouros et~al.(2024)]{fatouros2024marketsenseai}
Fatouros, G., Metaxas, K., Soldatos, J., and Kyriazis, D. (2024).
\newblock Can large language models beat wall street? {E}valuating {GPT-4}'s impact on financial decision-making with {MarketSenseAI}.
\newblock \emph{Neural Computing and Applications}, pages 1--26. doi:10.1007/s00521-024-10613-4.

\bibitem[Fatouros et~al.(2025)]{fatouros2025marketsenseai2}
Fatouros, G., Metaxas, K., Soldatos, J., and Karathanassis, M. (2025).
\newblock {MarketSenseAI 2.0}: Enhancing stock analysis through {LLM} agents.
\newblock \emph{IEEE International Conference on Data Mining Workshops (ICDMW '25)}, pages 883--892. arXiv:2502.00415.

\bibitem[Feng et~al.(2019)]{feng2018temporal}
Feng, F., He, X., Wang, X., Luo, C., Liu, Y., and Chua, T.-S. (2019).
\newblock Temporal relational ranking for stock prediction.
\newblock \emph{ACM Transactions on Information Systems}, 37(2):Article 27.

\bibitem[French(2025)]{french2025library}
French, K.~R. (2025).
\newblock Data library: Daily research returns, 5 factors, and momentum.
\newblock \url{https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html}.

\bibitem[Gao et~al.(2025)]{gao2025lookahead}
Gao, Z., Jiang, W., and Yan, Y. (2025).
\newblock A test of lookahead bias in {LLM} forecasts.
\newblock \emph{arXiv preprint arXiv:2512.23847}.

\bibitem[Gu et~al.(2020)]{gu2020empirical}
Gu, S., Kelly, B., and Xiu, D. (2020).
\newblock Empirical asset pricing via machine learning.
\newblock \emph{The Review of Financial Studies}, 33(5):2223--2273.

\bibitem[Guo et~al.(2025)]{guo2025mass}
Guo, T., Shen, H., Huang, J., Mao, Z., Luo, J., Chen, B., Chen, Z., Liu, X., Xia, B., Liu, L., Ma, Y., and Zhang, M. (2025).
\newblock {MASS}: Multi-agent simulation scaling for portfolio construction.
\newblock \emph{arXiv preprint arXiv:2505.10278}.

\bibitem[Hwang et~al.(2023)]{hwang2023stoploss}
Hwang, Y., Park, J., Lee, Y., and Lim, D.-Y. (2023).
\newblock Stop-loss adjusted labels for machine learning-based trading of risky assets.
\newblock \emph{Finance Research Letters}, 58(A):104285.

\bibitem[Hwang et~al.(2024)]{hwang2024simstock}
Hwang, Y., Zohren, S., and Lee, Y. (2024).
\newblock Temporal representation learning for stock similarities and its applications in investment management.
\newblock \emph{arXiv preprint arXiv:2407.13751}.

\bibitem[Hwang et~al.(2025)]{hwang2025dinn}
Hwang, Y., Kong, Y., Zohren, S., and Lee, Y. (2025).
\newblock Decision-informed neural networks with large language model integration for portfolio optimization.
\newblock \emph{arXiv preprint arXiv:2502.00828}.

\bibitem[Jegadeesh and Titman(1993)]{jegadeesh1993returns}
Jegadeesh, N. and Titman, S. (1993).
\newblock Returns to buying winners and selling losers: Implications for stock market efficiency.
\newblock \emph{The Journal of Finance}, 48(1):65--91.

\bibitem[Kim et~al.(2023)]{kim2023llmanalysts}
Kim, S., Kim, S., Kim, Y., Park, J., Kim, S., Kim, M., Sung, C.~H., Hong, J., and Lee, Y. (2023).
\newblock {LLMs} analyzing the analysts: Do {BERT} and {GPT} extract more value from financial analyst reports?
\newblock \emph{Proceedings of the Fourth ACM International Conference on AI in Finance (ICAIF '23)}, pages 383--391.

\bibitem[Kim et~al.(2024)]{kim2024llmforecast}
Kim, A., Muhn, M., and Nikolaev, V. (2024).
\newblock Financial statement analysis with large language models.
\newblock \emph{Working Paper}, University of Chicago Booth School of Business.

\bibitem[Kim et~al.(2025a)]{kim2025dsl}
Kim, J., Choi, S., Lee, Y., Kim, Y., Choi, Y., and Lee, Y. (2025a).
\newblock Decision by supervised learning with deep ensembles: A practical framework for robust portfolio optimization.
\newblock \emph{arXiv preprint arXiv:2503.13544}.

\bibitem[Kim et~al.(2025b)]{kim2025finaidata}
Kim, J., Kim, Y., Lee, Y., and Byun, H. (2025b).
\newblock {FinAI Data Assistant}: {LLM}-based financial database query processing with the {OpenAI} function calling {API}.
\newblock \emph{arXiv preprint arXiv:2510.14162}.

\bibitem[Kim et~al.(2025c)]{kim2025guruagents}
Kim, Y., Lee, Y., Kim, J., and Lee, Y. (2025c).
\newblock {GuruAgents}: Emulating wise investors with prompt-guided {LLM} agents.
\newblock \emph{arXiv preprint arXiv:2510.01664}.

\bibitem[Koijen and Levy(2026)]{koijen2026agentic}
Koijen, R.~S.~J. and Levy, B. (2026).
\newblock Assessing the benefits of optimized agentic {AI} systems for asset pricing.
\newblock \emph{SSRN working paper}.

\bibitem[Lee et~al.(2024)]{lee2024pfotgnrec}
Lee, Y., Kim, Y., Sanz-Cruzado, J., McCreadie, R., and Lee, Y. (2024).
\newblock Stock recommendations for individual investors: A temporal graph network approach with mean-variance efficient sampling.
\newblock \emph{Proceedings of the 5th ACM International Conference on AI in Finance (ICAIF '24)}, pages 795--803. doi:10.1145/3677052.3698662.

\bibitem[Lee et~al.(2025)]{lee2025llmbl}
Lee, Y., Kim, Y., Kim, J., Kim, S., and Lee, Y. (2025).
\newblock {LLM}-enhanced {B}lack-{L}itterman portfolio optimization.
\newblock \emph{arXiv preprint arXiv:2504.14345}.

\bibitem[Li et~al.(2025)]{li2025rdagent}
Li, Y., Yang, X., Yang, X., Xu, M., Wang, X., Liu, W., and Bian, J. (2025).
\newblock {R\&D-Agent-Quant}: A multi-agent framework for data-centric factors and model joint optimization.
\newblock \emph{arXiv preprint arXiv:2505.15155}.

\bibitem[Lopez-Lira and Tang(2023)]{lopez2023chatgpt}
Lopez-Lira, A. and Tang, Y. (2023).
\newblock Can {ChatGPT} forecast stock price movements? {R}eturn predictability and large language models.
\newblock \emph{Working Paper}, University of Florida.

\bibitem[Zhao et~al.(2025)]{lyu2025alphaagents}
Zhao, T., Lyu, J., Jones, S., Garber, H., Pasquali, S., and Mehta, D. (2025).
\newblock {AlphaAgents}: Large language model based multi-agents for equity portfolio constructions.
\newblock \emph{arXiv preprint arXiv:2508.11152}.

\bibitem[Merchant and Levy(2025)]{merchant2025lookahead}
Merchant, H. and Levy, B. (2025).
\newblock A fast and effective solution to the problem of look-ahead bias in {LLMs}.
\newblock \emph{NeurIPS 2025 Workshop: Generative AI in Finance}. arXiv:2512.06607.

\bibitem[Nie et~al.(2024)]{nie2024surveylargelanguagemodels}
Nie, Y., Kong, Y., Dong, X., Mulvey, J.~M., Poor, H.~V., Wen, Q., and Zohren, S. (2024).
\newblock A survey of large language models for financial applications: Progress, prospects and challenges.
\newblock \emph{arXiv preprint arXiv:2406.11903}.

\bibitem[Papasotiriou et~al.(2024)]{papasotiriou2024ai}
Papasotiriou, K., Sood, S., Reynolds, S., and Balch, T. (2024).
\newblock {AI} in investment analysis: {LLMs} for equity stock ratings.
\newblock \emph{Proceedings of the 5th ACM International Conference on AI in Finance (ICAIF '24)}, pages 419--427. arXiv:2411.00856.

\bibitem[Poh et~al.(2021)]{poh2021learning}
Poh, D., Lim, B., Zohren, S., and Roberts, S. (2021).
\newblock Building cross-sectional systematic strategies by learning to rank.
\newblock \emph{The Journal of Financial Data Science}, 3(2):70--86.

\bibitem[Qin et~al.(2024)]{qin2024pairwise}
Qin, Z., Jagerman, R., Hui, K., Zhuang, H., Wu, J., Yan, L., Shen, J., Liu, T., Liu, J., Metzler, D., Wang, X., and Bendersky, M. (2024).
\newblock Large language models are effective text rankers with pairwise ranking prompting.
\newblock \emph{Findings of NAACL 2024}, pages 1504--1518.

\bibitem[Ren et~al.(2025)]{ren2025selfcalibrated}
Ren, R., Wang, Y., Zhou, K., Zhao, W.~X., Wang, W., Liu, J., Wen, J.-R., and Chua, T.-S. (2025).
\newblock Self-calibrated listwise reranking with large language models.
\newblock \emph{Proceedings of The Web Conference 2025 (WWW '25)}.

\bibitem[Romanko et~al.(2023)]{romanko2023chatgptportfolio}
Romanko, O., Narayan, A., and Kwon, R.~H. (2023).
\newblock {ChatGPT}-based investment portfolio selection.
\newblock \emph{SN Operations Research Forum}, 4(4):1--27. doi:10.1007/s43069-023-00277-6.

\bibitem[Sakurai et~al.(2026)]{sakurai2026rura}
Sakurai, K., Ogawa, T., Haseyama, M., Anan, A., and Nakagawa, K. (2026).
\newblock Risk-aware utility re-ranking for financial asset recommendation.
\newblock \emph{Proceedings of the 19th ACM International Conference on Web Search and Data Mining (WSDM '26)}.

\bibitem[Sanz-Cruzado et~al.(2024)]{sanzcruzado2024fartrans}
Sanz-Cruzado, J., Droukas, N., and McCreadie, R. (2024).
\newblock {FAR-Trans}: An investment dataset for financial asset recommendation.
\newblock \emph{arXiv preprint arXiv:2407.08692}.

\bibitem[Sawhney et~al.(2021)]{sawhney2021sthan}
Sawhney, R., Agarwal, S., Wadhwa, A., Derr, T., and Shah, R.~R. (2021).
\newblock Stock selection via spatiotemporal hypergraph attention network: A learning to rank approach.
\newblock \emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 35(1):497--504.

\bibitem[Song et~al.(2017)]{song2017ltrsentiment}
Song, Q., Liu, A., and Yang, S.~Y. (2017).
\newblock Stock portfolio selection using learning-to-rank algorithms with news sentiment.
\newblock \emph{Neurocomputing}, 264:20--28.

\bibitem[Sun et~al.(2023)]{sun2023rankgpt}
Sun, W., Yan, L., Ma, X., Wang, S., Ren, P., Chen, Z., Yin, D., and Ren, Z. (2023).
\newblock Is {ChatGPT} good at search? Investigating large language models as re-ranking agents.
\newblock \emph{Proceedings of EMNLP 2023}. arXiv:2304.09542.

\bibitem[Tan et~al.(2024)]{tan2024llmchina}
Tan, L., Wu, H., and Zhang, X. (2024).
\newblock Large language models and return prediction in {China}.
\newblock \emph{SSRN Working Paper No.\ 4712248}.

\bibitem[Tang et~al.(2025)]{tang2025alphaagent}
Tang, Z., Chen, Z., Yang, J., Mai, J., Zheng, Y., Wang, K., Chen, J., and Lin, L. (2025).
\newblock {AlphaAgent}: {LLM}-driven alpha mining with regularized exploration to counteract alpha decay.
\newblock \emph{Proceedings of the 31st ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD '25)}. arXiv:2502.16789.

\bibitem[Xie et~al.(2023)]{xie2024wallstreetneophyte}
Xie, Q., Han, W., Lai, Y., Peng, M., and Huang, J. (2023).
\newblock The {W}all {S}treet {N}eophyte: A zero-shot analysis of {ChatGPT} over multimodal stock movement prediction challenges.
\newblock \emph{arXiv preprint arXiv:2304.05351}.

\bibitem[Xiao et~al.(2024)]{xiao2024tradingagents}
Xiao, Y., Sun, E., Luo, D., and Wang, W. (2024).
\newblock {TradingAgents}: Multi-agents {LLM} financial trading framework.
\newblock \emph{arXiv preprint arXiv:2412.20138}.

\bibitem[Yang et~al.(2024)]{yang2024finrobot}
Yang, H. et~al. (2024).
\newblock {FinRobot}: An open-source {AI} agent platform for financial applications using large language models.
\newblock \emph{arXiv preprint arXiv:2405.14767}.

\bibitem[Yu et~al.(2024)]{yu2024fincon}
Yu, Y. et~al. (2024).
\newblock {FinCon}: A synthesized {LLM} multi-agent system with conceptual verbal reinforcement for enhanced financial decision making.
\newblock \emph{arXiv preprint arXiv:2407.06567}.

\bibitem[Yu et~al.(2025)]{yu2025finmem}
Yu, Y., Li, H., Chen, Z., Jiang, Y., Li, Y., Suchow, J.~W., Zhang, D., and Khashanah, K. (2025).
\newblock {FINMEM}: A performance-enhanced {LLM} trading agent with layered memory and character design.
\newblock \emph{IEEE Transactions on Big Data}. doi:10.1109/TBDATA.2025.3593370.

\bibitem[Zhang et~al.(2022)]{zhang2022listwise}
Zhang, X., Wu, L., and Chen, Z. (2022).
\newblock Constructing long--short stock portfolio with a new listwise learn-to-rank algorithm.
\newblock \emph{Quantitative Finance}, 22(2):321--331.

\bibitem[Zhuang et~al.(2024)]{zhuang2024setwise}
Zhuang, S., Zhuang, H., Koopman, B., and Zuccon, G. (2024).
\newblock A setwise approach for effective and highly efficient zero-shot ranking with large language models.
\newblock \emph{Proceedings of SIGIR '24}.

\end{thebibliography}
}
